Weighing Chances and Use Against Risks and Misuse of Emerging Genome Analysis and Manipulation Technology

### 2022-05-31 draft.tex

\section{Conclusion}
Since the Assyrians and Mendel, a long time has passed. The development of Genome Analysis has become cheaper and is useful in many areas. The police can identify criminals more quickly, doctors can identify illnesses at an early stage and private individuals can learn more about their origins and personality.

@@

\end{thebibliography}

\end{document}

>>>>

\section{Conclusion}
Since the Assyrians and Mendel, a long time has passed. The development of Genome Analysis has become cheaper and is useful in many areas. The police can identify criminals more quickly, doctors can identify illnesses at an early stage and private individuals can learn more about their origins and personality.
Other controversial topics are the general data storage of sensitive DNA data, transparency regarding access by third parties and possibilities for deletion of DNA profiles. In many areas, more emphasis is placed on the collection of data than on the responsible handling of it and the deletion of useless DNA profiles, which makes it potentially easier to misuse the data.

@@

\end{thebibliography}
\end{document}
